Paper Plots V2

### 2025-02-28 Rmd/paper_plots/paper_plots_1.3.Rmd
clean up change_length_N, git new scenarios, mark DEV combine post strata work to come back to later.

### Min 20
```{r, fig.width=9, fig.height=5}
out_26.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_26.1_ISS_500iters_output_2025-02-27.RDS")

@@

df %>% 
  tidytable::mutate(ISS.error = (iss.20.min - iss.base)/iss.base) %>% 
  filter(year%in%2023) %>% 
  select(ISS.error) %>% 
  boxplot()

>>>>

### Min 20
```{r, fig.width=9, fig.height=5}

## min(20, #samples) port and haul 1999-2023
# with replacement
out_26.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_26.1_ISS_500iters_output_2025-02-27.RDS")

@@

# without replacement - THIS HAS MUCH SMALLER PERCENT DIFFERENCE! So use this in paper. 
out_27.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_27.1_ISS_500iters_output_2025-02-28.RDS")

year = out_27.1$length$iss$YEAR

df = tidytable(year = year,
               iss.base = out_1.4$length$iss$iss,
               iss.20.min = out_27.1$length$iss$iss)

# without replacement - Hauls only 
out_28.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_28.1_ISS_500iters_output_2025-02-28.RDS")

year = out_28.1$length$iss$YEAR

df = tidytable(year = year,
               iss.base = out_1.4$length$iss$iss,
               iss.20.min = out_28.1$length$iss$iss)
